%% Compile using latex engine, TeX 2019 distro.
%% Template for ENG 401 reports
%% by Robin Turner
%% Adapted from the IEEE peer review template
%% https://www.overleaf.com/latex/templates/latex-template-for-technical-report/qtznkrpkjybm

\documentclass[peerreview]{IEEEtran}
\usepackage{cite}                    % Tidies up citation numbers.
\usepackage{url}                     % Provides better formatting of URLs.
\usepackage{booktabs}                % Allows the use of \toprule, \midrule and \bottomrule in tables for horizontal lines
\usepackage{float}

% https://tex.stackexchange.com/questions/120291/arabic-in-latex
\usepackage{arabtex}
\usepackage{utf8}

% https://tex.stackexchange.com/questions/101964/change-font-size-in-arabtex-package
%%% from Uxnsh.fd
\DeclareFontFamily{U}{xnsh}{}%

\DeclareFontShape{U}{xnsh}{m}{n}{%                                   
   <-6> sfixed * [6.0] xnsh14
      <6-10> s * [1.20] xnsh14
         <10><10.95><12><14.4><17.28><20.74><24.88> s * [1.20] xnsh14
         }{}

\DeclareFontShape{U}{xnsh}{bx}{n}{%
   <-6> sfixed * [6.0] xnsh14bf
   <6-10> s * [1.20] xnsh14bf
   <10><10.95><12><14.4><17.28><20.74><24.88> s * [1.20] xnsh14bf
}{}
%%% end of added code

% https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\hyphenation{op-tical net-works semi-conduc-tor} % Corrects some bad hyphenation 

\begin{document}

%start encoding to Unicode
%Note that your layout must support Arabic text when compiling
\setcode{utf8}
%To start typing in Arabic use the command arabtext

% \begin{titlepage}
% paper title
% can use line-breaks \\ within to get better formatting as desired
\title{An Easy Approach to Technical Writing}

% author names and affiliations
\author{Ahmed Waleed \\
Co-authors: Amr El Begawy, Marwan Ashraf \\
Department of Computer Engineering\\
Alexandria University\\
}
\date{December 29, 2019}

% make the title area
\maketitle
\tableofcontents
\listoffigures
\listoftables
% \end{titlepage}

\IEEEpeerreviewmaketitle

\begin{abstract}
% How to Write an Abstract for a Research Paper: https://youtu.be/JMEnRBss6V4
% Motivation
Technical reports are usually written according to general standards, corporate design standards of the current university or company, logical rules, and practical experiences.
% Problems
These rules are not known well enough among writing engineers and technicians. Therefore, this summary intends to help you create technical reports.
    Such an interesting topic, many students struggle to get started with.
% Methods
    Using rules and guidelines contained, you will be introduced to all the
    basic technical writing concepts.
\end{abstract}

\section{Technical Reports Writing\cite{Lec1}}
Technical writing is a style of formal writing used in many fields to explain technology and related ideas to:
\begin{itemize}
\item Specific technical, general technical or non-technical audiences.
\end{itemize}
\vspace{-5mm}   % Reduce white space

\subsection{Characteristics of Good Technical Writing}

% https://www.overleaf.com/learn/latex/Text_alignment
\begin{flushright}
    \leavevmode\\[-2mm]
    \begin{tabular}{|p{1.3cm} p{0.1cm} p{5.5cm}|}
        \hline
        \multicolumn{3}{c}{}\\[-1em]
        Accurate   &: & conforms to truth or fact.\\
        Clear      &: & simple and direct sentences.\\
        Concise    &: & use of a minimum of words.\\
        Coherent   &: & easy-to-follow line of thinking.\\
        Accessible &: & consists of small independent sections.\\
        \multicolumn{3}{c}{}\\[-1em]
        \hline
    \end{tabular}
\end{flushright}

\subsection{Converting to Technical Writing}
Suppose you are writing a report where you may not use ``I'', or you are writing about a sentence subject that can not actually do anything. What to do when the passive voice is the best, most natural choice?
The answer lies in writing direct sentences—in passive voice—that have simple subjects and verbs.\cite{reference_style}

% https://www.overleaf.com/learn/latex/Text_alignment
\begin{flushright}
    \small
    \leavevmode\\[-2mm]
    \begin{tabular}{|p{3.41cm} p{0.1cm} p{3.4cm}|}
        \hline
        \multicolumn{3}{c}{}\\[-3mm]
        I conducted a tensile test at room temperature because & $\rightarrow$ &  A tensile test was conducted.\\
        I needed to find out a baseline \ for \ tensile \ strength. & $\rightarrow$ &  Baseline tensile strength was established.\\
        I followed ASTM specification E8M for testing. & $\rightarrow$ &  ASTM Specification E8M was followed.\\
        \multicolumn{3}{c}{}\\[-3mm]
        \hline
    \end{tabular}
    \\[+1mm]
    Using passive voice does not have to create ambiguity.
\end{flushright}

\section{The Writing Process\cite{Lec2}}

\appendices

\section{Elementary Rules\cite{reference_bartleby}}
Asserting that one must first know the rules to break them, ``Elements of Style'' is a must-have reference book for any student and conscientious writer. Intended for use in which the practice of composition is combined with the study of literature, it gives in brief space the principal requirements of plain English style and concentrates attention on the rules of usage and principles of composition most commonly violated.

\section{Vocabulary}

\begin{table}[H]
\centering
% https://texblog.org/2019/06/03/control-the-width-of-table-columns-tabular-in-latex/
\begin{tabular}{|p{3cm}|p{3cm}|}
 \hline
 &\\[-1em]
 Word & \begin{arabtext} الترجمة \end{arabtext} \\[-1em]
 \hline\hline
 &\\[-1em]
 Accurate & \begin{arabtext} دقيق \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Clear & \begin{arabtext} واضح \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Concise & \begin{arabtext} مختصر \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Coherent & \begin{arabtext} مترابط \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Accessible & \begin{arabtext} سهل الوصول \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Conducted & \begin{arabtext} أجرى ، أدى \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Tensile & \begin{arabtext} شد \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Baseline & \begin{arabtext} حدود \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Ambiguity & \begin{arabtext} غموض ، التباس \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Others & \begin{arabtext} أخرى \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Others & \begin{arabtext} أخرى \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Others & \begin{arabtext} أخرى \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Others & \begin{arabtext} أخرى \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Others & \begin{arabtext} أخرى \end{arabtext} \\[-1em]
 \hline
  &\\[-1em]
 Others & \begin{arabtext} أخرى \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Conscientious & \begin{arabtext} عنده ضمير \end{arabtext} \\[-1em]
 \hline
 ... & \multicolumn{1}{r}{...} \\
\end{tabular}
\smallskip 
\caption{Translation}
\end{table}     

\begin{thebibliography}{1}

\bibitem{Lec1}``Technical Reports Writing,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec1_TW}.
\bibitem{Lec2}``The Writing Process,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec2_TW}.
\bibitem{Lec3}``Document Editing I,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec3_TW}.
\bibitem{Lec4}``Document Editing II,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec4_TW}.
\bibitem{Lec5}``CVs and Covering Letters,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec5_TW}.
\bibitem{Lec6}``Collaborative Writing,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec6_TW}.
\bibitem{Lec7}``Instructions and Manuals,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec7_TW}.
\bibitem{Lec8}``Oral Presentations,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec8_TW}.
\\[-1mm]
\bibitem{LecB}``Writing A Good Technical Paper,''\\ Dr. Moustafa Youssef, 2019. [Lecture]: \url{http://bit.ly/LecB_TW}.
\\[-1mm]
\bibitem{reference_springer1}``How to Write Technical Reports,'' Heike Hering, 2019. \\[0mm] [E-book]: \url{https://doi.org/10.1007/978-3-662-58107-0}.
\bibitem{reference_springer2}``The Craft of Scientific Writing,'' Michael Alley, 2018. \\[0mm] [E-book]: \url{https://doi.org/10.1007/978-1-4419-8288-9}.
\bibitem{reference_springer3}``User Guides, Manuals, and Technical Writing,'' Wallwork, 2014. \\[0mm] [E-book]: \url{https://doi.org/10.1007/978-1-4939-0641-3}.
\\[-1mm]
\bibitem{reference_bartleby}``The Elements of Style,'' Bartleby, William Strunk, 1918. \\[0mm] [Online-book]: \url{https://www.bartleby.com/141/}.
\bibitem{reference_style}``Effective Technical Writing in the Information Age,'' Joe Schall. \\[0mm] [Online-book]: \url{https://www.e-education.psu.edu/styleforstudents/node/1787/}.

\end{thebibliography}

\end{document}