%% Template for ENG 401 reports
%% by Robin Turner
%% Adapted from the IEEE peer review template
%% https://www.overleaf.com/latex/templates/latex-template-for-technical-report/qtznkrpkjybm

\documentclass[peerreview]{IEEEtran}
\usepackage{cite}                    % Tidies up citation numbers.
\usepackage{url}                     % Provides better formatting of URLs.
\usepackage[utf8]{inputenc}          % Allows Turkish characters.
\usepackage{booktabs}                % Allows the use of \toprule, \midrule and \bottomrule in tables for horizontal lines
\usepackage{graphicx}
\usepackage{float}

%In the preamble section include the arabtex and utf8 packages
\usepackage{arabtex}
\usepackage{utf8}

% https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\hyphenation{op-tical net-works semi-conduc-tor} % Corrects some bad hyphenation 

\begin{document}
% \begin{titlepage}
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An Easy Approach to Technical Writing}

% author names and affiliations
\author{Ahmed Waleed \\
Co-authors: Amr El Begawy, Marwan Ashraf \\
Department of Computer Engineering\\
Alexandria University\\
}
\date{December 29, 2019}

% make the title area
\maketitle
\tableofcontents
\listoffigures
\listoftables
% \end{titlepage}

\IEEEpeerreviewmaketitle

\begin{abstract}
% How to Write an Abstract for a Research Paper: https://youtu.be/JMEnRBss6V4
% Motivation
Technical reports are usually written according to general standards, corporate design standards of the current university or company, logical rules, and practical experiences.
% Problems
These rules are not known well enough among writing engineers and technicians. Therefore, this summary intends to help you create technical reports.
    Such an interesting topic, many students struggle to get started with.
% Methods
    Using rules and guidelines contained, you will be introduced to all the
    basic technical writing concepts.
\end{abstract}

\section{Technical Reports Writing\cite{Lec1}}
    
\subsection{Subsection}

\begin{thebibliography}{1}

\bibitem{Lec1}``Technical Reports Writing,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec1_TW}.
\bibitem{Lec2}``The Writing Process,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec2_TW}.
\bibitem{Lec3}``Document Editing I,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec3_TW}.
\bibitem{Lec4}``Document Editing II,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec4_TW}.
\bibitem{Lec5}``CVs and Covering Letters,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec5_TW}.
\bibitem{Lec6}``Collaborative Writing,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec6_TW}.
\bibitem{Lec7}``Instructions and Manuals,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec7_TW}.
\bibitem{Lec8}``Oral Presentations,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec8_TW}.
\\[-1mm]
\bibitem{LecB}``Writing A Good Technical Paper,''\\ Dr. Moustafa Youssef, 2019. [Lecture]: \url{http://bit.ly/LecB_TW}.
\\[-1mm]
\bibitem{reference}``How to Write Technical Reports,'' Springer, Heike Hering, 2019. \\[0mm] [E-book]: \url{https://doi.org/10.1007/978-3-662-58107-0}.

\end{thebibliography}

\end{document}