%% Compile using latex engine, TeX 2019 distro.
%% Template for ENG 401 reports
%% by Robin Turner
%% Adapted from the IEEE peer review template
%% https://www.overleaf.com/latex/templates/latex-template-for-technical-report/qtznkrpkjybm

\documentclass[peerreview]{IEEEtran}
\usepackage{cite}                    % Tidies up citation numbers.
\usepackage{url}                     % Provides better formatting of URLs.
\usepackage{booktabs}                % Allows the use of \toprule, \midrule and \bottomrule in tables for horizontal lines
\usepackage{float}

% https://tex.stackexchange.com/questions/120291/arabic-in-latex
\usepackage{arabtex}
\usepackage{utf8}

% https://tex.stackexchange.com/questions/101964/change-font-size-in-arabtex-package
%%% from Uxnsh.fd
\DeclareFontFamily{U}{xnsh}{}%

\DeclareFontShape{U}{xnsh}{m}{n}{%                                   
   <-6> sfixed * [6.0] xnsh14
      <6-10> s * [1.20] xnsh14
         <10><10.95><12><14.4><17.28><20.74><24.88> s * [1.20] xnsh14
         }{}

\DeclareFontShape{U}{xnsh}{bx}{n}{%
   <-6> sfixed * [6.0] xnsh14bf
   <6-10> s * [1.20] xnsh14bf
   <10><10.95><12><14.4><17.28><20.74><24.88> s * [1.20] xnsh14bf
}{}
%%% end of added code

% https://tex.stackexchange.com/questions/3033/forcing-linebreaks-in-url
\PassOptionsToPackage{hyphens}{url}\usepackage{hyperref}

\hyphenation{op-tical net-works semi-conduc-tor} % Corrects some bad hyphenation 

\begin{document}

%start encoding to unicode
%Note that your layout must support arabic text when compiling
\setcode{utf8}
%To start typing in Arabic use the command arabtext

% \begin{titlepage}
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{An Easy Approach to Technical Writing}

% author names and affiliations
\author{Ahmed Waleed \\
Co-authors: Amr El Begawy, Marwan Ashraf \\
Department of Computer Engineering\\
Alexandria University\\
}
\date{December 29, 2019}

% make the title area
\maketitle
\tableofcontents
\listoffigures
\listoftables
% \end{titlepage}

\IEEEpeerreviewmaketitle

\begin{abstract}
% How to Write an Abstract for a Research Paper: https://youtu.be/JMEnRBss6V4
% Motivation
Technical reports are usually written according to general standards, corporate design standards of the current university or company, logical rules, and practical experiences.
% Problems
These rules are not known well enough among writing engineers and technicians. Therefore, this summary intends to help you create technical reports.
    Such an interesting topic, many students struggle to get started with.
% Methods
    Using rules and guidelines contained, you will be introduced to all the
    basic technical writing concepts.
\end{abstract}

\section{Technical Reports Writing\cite{Lec1}}
Technical writing is a style of formal writing used in many fields to explain technology and related ideas to:
\begin{itemize}
\item Specific technical, general technical or non-technical audiences.
\end{itemize}
\vspace{-5mm}   % Reduce white space

\subsection{Characteristics of Good Technical Writing}

% https://www.overleaf.com/learn/latex/Text_alignment
\begin{flushright}
    \leavevmode\\[-2mm]
    \begin{tabular}{|l p{5.5cm}|}
        \hline
        \multicolumn{2}{c}{}\\[-1em]
        Accurate: & conforms to truth or fact.\\
        Clear:    & simple and direct sentences.\\
        Concise:  & use of a minimum of words.\\
        Coherent: & easy-to-follow line of thinking.\\
        Accessible: & consists of small independent sections.\\
        \multicolumn{2}{c}{}\\[-1em]
        \hline
    \end{tabular}
\end{flushright}

\subsection{Converting to Technical Writing}


\section{The Writing Process\cite{Lec2}}

\appendices

\section{Vocabulary}

\begin{table}[H]
\centering
% https://texblog.org/2019/06/03/control-the-width-of-table-columns-tabular-in-latex/
\begin{tabular}{|p{3cm}|p{3cm}|}
 \hline
 &\\[-1em]
 Word & \begin{arabtext} الترجمة \end{arabtext} \\[-1em]
 \hline\hline
 &\\[-1em]
 Accurate & \begin{arabtext} دقيق \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Clear & \begin{arabtext} واضح \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Concise & \begin{arabtext} مختصر \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Coherent & \begin{arabtext} مترابط \end{arabtext} \\[-1em]
 \hline
 &\\[-1em]
 Accessible & \begin{arabtext} سهل الوصول \end{arabtext} \\[-1em]
 \hline
 ... & \multicolumn{1}{r}{...} \\
\end{tabular}
\smallskip 
\caption{Translation}
\end{table}     
% https://mylatexnotes.wordpress.com/2017/09/13/table-remove-white-space-after-table/

\section{Elementary Rules of Usage\cite{reference_bartleby}}

\section{What Goes in the Appendices}
The appendix is for material that readers only need to know if they are studying the report in depth. Relevant charts, big tables of data, large maps, graphs, etc. that were part of the research, but would distract the flow of the report should be given in the Appendices. 
\section{Formatting the Appendices}
Each appendix needs to be given a letter (A, B, C, etc.) and a title. \LaTeX will do the lettering automatically.

\begin{thebibliography}{1}

\bibitem{Lec1}``Technical Reports Writing,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec1_TW}.
\bibitem{Lec2}``The Writing Process,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec2_TW}.
\bibitem{Lec3}``Document Editing I,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec3_TW}.
\bibitem{Lec4}``Document Editing II,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec4_TW}.
\bibitem{Lec5}``CVs and Covering Letters,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec5_TW}.
\bibitem{Lec6}``Collaborative Writing,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec6_TW}.
\bibitem{Lec7}``Instructions and Manuals,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec7_TW}.
\bibitem{Lec8}``Oral Presentations,''\\ Dr. Nagia Ghanem, 2019. [Lecture]: \url{http://bit.ly/Lec8_TW}.
\\[-1mm]
\bibitem{LecB}``Writing A Good Technical Paper,''\\ Dr. Moustafa Youssef, 2019. [Lecture]: \url{http://bit.ly/LecB_TW}.
\\[-1mm]
\bibitem{reference_springer}``How to Write Technical Reports,'' Springer, Heike Hering, 2019. \\[0mm] [E-book]: \url{https://doi.org/10.1007/978-3-662-58107-0}.
\bibitem{reference_bartleby}``The Elements of Style,'' Bartleby, William Strunk, 1999. \\[0mm] [E-book]: \url{https://www.bartleby.com/141/}.

\end{thebibliography}

\end{document}